Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-06-10 Manuscript/proto-manuscript.tex
fix: added bracket

Because the biologically relevant cations like \ce{Na^+} and \ce{Ca^{2+}
are found to interact only with the phospholipid head group,
and the accuracy of alkyl sidechains in Lipid14 model are satisfactory, 
we exclude alkyl tails from our modifications.

>>>>

Because the biologically relevant cations like \ce{Na^+} and \ce{Ca^{2+}}
are found to interact only with the phospholipid head group,
and the accuracy of alkyl sidechains in Lipid14 model are satisfactory, 
we exclude alkyl tails from our modifications.
